% Article-aligned captions for archived PDF figures.
\newcommand{\FigOneCaption}{Primary KAP values measured in the normalized interval $R\leq R_{\rm h,l}$. Negative KAP denotes projected radial squared-dispersion excess and positive KAP denotes tangential excess. Five clusters satisfy the analytic two-sided $2\sigma$ radial criterion; none satisfies the tangential criterion. Error bars show $1\sigma$ uncertainties.}
\newcommand{\FigTwoCaption}{Empirical GKI measurements in $R\leq R_{\rm h,l}$. GKI is the outward logarithmic slope $d\ln\sigma/d\ln R$ over the fitted interval. Eighteen measurements are significantly negative, while NGC~5927 and NGC~6441 are flat/zero-consistent. Error bars show $1\sigma$ uncertainties.}
\newcommand{\FigThreeCaption}{Raw and noise-aware anisotropy-profile scatter diagnostics in $R\leq R_{\rm h,l}$. The quantities are profile-inspection diagnostics and do not define physical severity classes.}
\newcommand{\FigBOneCaption}{Combined, projected radial, and projected tangential proper-motion dispersion profiles for all 20 clusters. The dashed line marks $R_{\rm h,l}$; black, blue, and orange curves denote $\sigma$, $\sigma_r$, and $\sigma_t$.}
\newcommand{\FigBTwoCaption}{Bin-wise projected $\beta(R)$ profiles for all 20 clusters. Bin-to-bin variation may reflect physical structure, measurement uncertainty, population mixing, or residual systematics and should be interpreted with $D_s$ and $D_{s,\rm corr}$.}
\newcommand{\FigBThreeCaption}{Relation between KAP and normalized projected-anisotropy contrasts over the full HST radial range. The dispersion-scale-weighted construction is algebraically identical to KAP.}
\newcommand{\FigBFourCaption}{Sensitivity of KAP and GKI to the adopted radial interval. Full-HST-range values are compared with $R\leq R_{\rm h,l}$ values; NGC~6388 and NGC~6441 change KAP significance class.}
